A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-10-01 journal/metrics.tex
small fixes' git push

For every failing test case, its response to mutants defines a bit-vector, with
length equal to the number of mutants that repaired any test case,
where a 1 bit indicates that the mutant in question repairs this test
case\footnote{By \emph{repairing} a failing test we here mean that a mutant
causes the test to pass, \emph{and} the mutant does not cause
other, previously passing tests, to fail.}.  These cannot be effectively compared with Hamming distance. Consider $t_1$ and $t_2$, both repaired
by 100 mutants.  If these two test cases share 90 common repairing
mutants, and disagree for 10, they have a Hamming
distance of 20.  This makes them ``less similar'' than two test cases,
$t_1'$ and $t_2'$, where $t_1'$ is repaired by 5 mutants, $t_2'$ is
repaired by 5 mutants, and \emph{none of those mutants overlap.}   A Jaccard distance, also used (as similarity) in some fault
localization algorithms \cite{Pinpoint}, is a better fit.  For bitvectors $u$ and $v$ of length $n$:
%\vspace{-0.08in}
\[d(u,v) = 
\begin{cases}
\frac{\sum_{i=0}^{n-1} 1\ \text{if}\ u_i \neq v_i\ \text{else}\ 0}{\sum_{i=0}^{n-1} 1
\  \text{if}\ u_i \neq 0 \vee v_i \neq 0\ \text{else}\ 0} & \exists i:u_i\neq 0 \vee v_i\neq 0\\
0 & otherwise
\end{cases}
\]

>>>>

For every failing test case, the response (fixing or not fixing the
failure) to all mutants defines a bitvector, with
length equal to the number of mutants that repaired \emph{any} test
case (or all mutants; it does not matter for our proposed metric),
where a 1 bit indicates that the mutant in question repairs this test
case\footnote{By \emph{repairing} a failing test we here mean that a mutant
causes the test to pass, \emph{and} the mutant does not cause
other, previously passing tests, to fail.}.  These bitvectors cannot be effectively compared with Hamming distance. Consider $t_1$ and $t_2$, both repaired
by 100 mutants.  If these two test cases share 90 common repairing
mutants, and disagree for 10, they have a Hamming
distance of 20.  This makes them ``less similar'' than two test cases,
$t_1'$ and $t_2'$, where $t_1'$ is repaired by 5 mutants, $t_2'$ is
repaired by 5 mutants, and \emph{none of those mutants overlap.}   A Jaccard distance, also used (as similarity) in some fault
localization algorithms \cite{Pinpoint}, is a better fit.  For bitvectors $u$ and $v$ of length $n$:
%\vspace{-0.08in}
\[d(u,v) = 
\begin{cases}
\frac{\sum_{i=0}^{n-1} 1\ \text{if}\ u_i \neq v_i\ \text{else}\ 0}{\sum_{i=0}^{n-1} 1
\  \text{if}\ u_i \neq 0 \vee v_i \neq 0\ \text{else}\ 0} & \exists i:u_i\neq 0 \vee v_i\neq 0\\
0 & otherwise
\end{cases}
\]
